### 2023-06-17 manuscript.tex
No need for _site clone [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/f615459f766ae8625991bc1f1e3f980a17b606ba.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/f615459f766ae8625991bc1f1e3f980a17b606ba/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5298666326

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/86cfd89b9215552dadcb75065d595d3e7c1d6c42/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/86cfd89b9215552dadcb75065d595d3e7c1d6c42}{stain/2022-fdo-paper@86cfd89}
on June 17, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f615459f766ae8625991bc1f1e3f980a17b606ba/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f615459f766ae8625991bc1f1e3f980a17b606ba}{stain/2022-fdo-paper@f615459}
on June 17, 2023.
